### 2018-03-27 Writing/draft.tex
Updated final results

The overall amount of character difference in a matrix has an effect of the ability to recover the correct topology with maximising character difference leading to the smallest loss in phylogenetic information (median $NTS_{RF}$ = 0.95 and median $NTS_{Tr}$ = 0.96) followed by simply randomising the characters (median $NTS_{RF}$ = 0.79 and median $NTS_{Tr}$ = 0.72) and minimising the character difference (median $NTS_{RF}$ = 0.6 and median $NTS_{Tr}$ = 0.28 - see Supplementary material 3 for the full summary statistics).
There is a significant difference between all scenarios (maximising, minimising and randomising) with the highest probability of overlap being between maximising and randomising the character difference (Bhattacharrya Coefficient of 0.89 for the $NTS_{RF}$ and 0.92 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test}) and the lowest probability between maximising and minimising the character difference (Bhattacharrya coefficient of 0.59 for the $NTS_{RF}$ and 0.63 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test})

@@

\subsubsection{Number of characters}
This effect of the character difference is not dependent on the number of characters when looking at clade conservation (i.e. $NTS_{RF}$).
The median $NTS_{RF}$ was similar for 100, 350 and 1000 characters (0.76, 0.78, 0.8 respectively - see supplementary materials 3) with a significant difference only between 100 and 1000 characters (Table \ref{Tab_pooledscharacters_test}).
%MB: The above sentence has too many "for"s. It's too long and needs to be split to be intelligible.
%TG: fix attempt
The number of characters affects the character difference more in terms of taxon placement for a low number of characters (median $NTS_{RF}$ for 100, 350 and 1000 characters equals 0.54, 0.70, 0.76 respectively - see supplementary materials 3) with a significant difference between 100 and 350 or 1000 characters (Table \ref{Tab_pooledscharacters_test}).
However, these differences have to be contrasted by a very high probability of overlap between each number of characters and metrics (Bhattacharrya Coefficient always $>0.95$) suggesting that the significant effects of the number of characters still leads to really similar distributions.

@@

Similar to the effect of number of characters on character difference, the number of taxa seems to have only a marginal effect.
A low number of taxa (25) resulted in significant differences in both $NTS_{RF}$ and $NTS_{Tr}$ (medians for 25, 75 and 150 taxa equals 0.8, 0.76, 0.75 $NTS_{RF}$ and 0.75, 0.59 and 0.59 $NTS_{Tr}$respectively - Table \ref{Tab_pooledstaxa_test} and see supplementary materials 3).
Again, however, the significant differences have to be contrasted with still high probabilities of overlaps for each $NTS_{RF}$ and $NTS_{Tr}$ distributions for every number of taxa (Table \ref{Tab_pooledstaxa_test}).

@@

Regarding the inference method, there is a significant difference in clade conservation between Bayesian and maximum parsimony (Table \ref{Tab_pooledsmethods_test} - median $NTS_{RF}$ of 0.82 and 0.68 respectively) but not in terms of individual taxon placements (Table \ref{Tab_pooledsmethods_test} - median $NTS_{Tr}$ of 0.72 and 0.61 respectively).

>>>>

The overall amount of character difference in a matrix has an effect of the ability to recover the correct topology when maximising character difference leading to the smallest loss in phylogenetic information (median $NTS_{RF}$ = 0.956 and median $NTS_{Tr}$ = 0.839) followed by simply randomising the characters (median $NTS_{RF}$ = 0.762 and median $NTS_{Tr}$ = 0.628) and minimising the character difference (median $NTS_{RF}$ = 0.605 and median $NTS_{Tr}$ = 0.303 - see Supplementary material 3 for the full summary statistics).
There is a significant difference between all scenarios (maximising, minimising and randomising) with the highest probability of overlap being between maximising and randomising the character difference (Bhattacharrya Coefficient of 0.873 for the $NTS_{RF}$ and 0.908 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test}) and the lowest probability between maximising and minimising the character difference (Bhattacharrya coefficient of 0.573 for the $NTS_{RF}$ and 0.614 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test})

@@

\subsubsection{Number of characters}
This effect of the character difference is not dependent on the number of characters when looking at clade conservation (i.e. $NTS_{RF}$).
The median $NTS_{RF}$ was similar for 100, 350 and 1000 characters (0.730, 0.745, 0.767 respectively - see supplementary materials 3) with a significant difference only between 100 and 1000 and 350 and 1000 characters (Table \ref{Tab_pooledscharacters_test}).
%MB: The above sentence has too many "for"s. It's too long and needs to be split to be intelligible.
%TG: fix attempt
The number of characters affects the character difference more in terms of taxon placement for a low number of characters (median $NTS_{Tr}$ for 100, 350 and 1000 characters equals 0.544, 0.693, 0.799 respectively - see supplementary materials 3) with a significant difference between 100 and 350 or 1000 characters (Table \ref{Tab_pooledscharacters_test}).
However, these differences have to be contrasted by a very high probability of overlap between each number of characters and metrics (Bhattacharrya Coefficient always $>0.95$) suggesting that the significant effects of the number of characters still leads to really similar distributions.

@@

Similar to the effect of number of characters on character difference, the number of taxa seems to have only a marginal effect.
A low number of taxa (25) resulted in significant differences with both 75 or 150 taxa in both $NTS_{RF}$ and $NTS_{Tr}$ but no differences between 75 and 150 taxa (medians for 25, 75 and 150 taxa equals 0.802, 0.76, 0.763 $NTS_{RF}$ and 0.758, 0.588 and 0.615 $NTS_{Tr}$ respectively - Table \ref{Tab_pooledstaxa_test} and see supplementary materials 3).
Again, however, the significant differences have to be contrasted with still high probabilities of overlaps for each $NTS_{RF}$ and $NTS_{Tr}$ distributions for every number of taxa (Table \ref{Tab_pooledstaxa_test}).

@@

Regarding the inference method, there is a significant difference in clade conservation between Bayesian and maximum parsimony (Table \ref{Tab_pooledsmethods_test} - median $NTS_{RF}$ of 0.828 and 0.679 respectively) but not in terms of individual taxon placements (Table \ref{Tab_pooledsmethods_test} - median $NTS_{Tr}$ of 0.738 and 0.601 respectively).
